neonstore: a local, provenance-aware workflow for NEON data

### 2020-09-09 paper/paper.Rmd
paper :pen:

---
title: "taxadb: A High-Performance Local Taxonomic Database Interface"
author:
  - name: "Carl Boettiger"
    affiliation: ucb
  - name: "Christine Laney"
    affiliation: neon
  - name: "Quinn Thomas"
    affiliation: vt
address:
  - code: ucb
    address: "Dept of Environmental Science, Policy, and Management, University of California Berkeley, Berkeley CA 94720-3114, USA"
  - code: neon
    address: "NEON"
  - code: vt
    address: "Virginia Tech"
abstract: |
  The National Ecological Observatory Network
journal: "TBD"
date: "`r Sys.Date()`"
bibliography: refs.bib
layout: 3p
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output: rticles::elsevier_article
---

@@

`neon_index()` takes optional arguments such as `product`, `start_date`, `end_date`, and `site` to allow for convenient sub-setting.  Because most observational and instrument-based products are divided by site and month, this is still not a convenient way to browse the data.  The helper function, `neon_store()`, summarizes products that all share the same file description and can thus be easily stacked.  Like `neon_index()`, optional arguments can filter the results to specific products, dates, and sites.

```{r}
neon_store()
```

In this example, we recognize several tables corresponding to the NEON bird survey, product `DP01.10003.001` (all prefixed with `brd_`).  We can read in all the individual files

@@

```{r message=FALSE}
write.csv(raw_files, "index.csv")
zip("brd_countdata.zip", raw_files$path)
```

>>>>

---
title: "neonstore: a local, provenance-aware workflow for NEON data"
author:
  - name: "Carl Boettiger"
    affiliation: ucb
  - name: "Quinn Thomas"
    affiliation: vt
  - name: "Christine Laney"
    affiliation: neon
  - name: "Claire Lunch"
    affiliation: neon

address:
  - code: ucb
    address: "Dept of Environmental Science, Policy, and Management, University of California Berkeley, Berkeley CA 94720-3114, USA"
  - code: neon
    address: "NEON"
  - code: vt
    address: "Virginia Tech"
abstract: |
  The National Ecological Observatory Network
journal: "Ecoinformatics"
date: "`r Sys.Date()`"
bibliography: refs.bib
layout: 3p
header-includes:
   - \usepackage{lineno}
   - \linenumbers
output: rticles::elsevier_article
---

@@

`neon_index()` takes optional arguments such as `product`, `start_date`, `end_date`, and `site` to allow for convenient sub-setting.  Because most observational and instrument-based products are divided by site and month, this is still not a convenient way to browse the data.

We can read in all the individual files

@@

```{r message=FALSE}
write.csv(raw_files, "index.csv")
neon_export("brd_countdata.zip")
```
